---
title: "p8105_hw1_mmu2108"
output: github_document
date: "2022-09-15"
---

```{r penguindata, message = FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

# Problem 1

-   The dataset "penguins" has 8 variables detailing penguin species, island found, measurements of the penguin's bill, flipper, and body mass, sex, and year found.
-   There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.
-   Mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("q1_plot.pdf")
```

# Problem 2

```{r q2}
q2 =
  tibble(
    rand_samp = rnorm(n = 10),
    rand_samp_pos = rand_samp > 0,
    char_vect = character(length = 10),
    factor_vect = factor(rand_samp, levels = 1:3)
  )
  
mean_rand_samp = mean(pull(q2, rand_samp))
mean_rand_samp_pos = mean(pull(q2, rand_samp_pos))
mean_char_vect = mean(pull(q2, char_vect))
mean_factor_vect = mean(pull(q2, factor_vect))
```

-   Mean of the random sample is `r mean_rand_samp`.
-   Mean of the logical sample is `r mean_rand_samp_pos`.
-   Mean of the random sample is `r mean_char_vect`.
-   Mean of the random sample is `r mean_factor_vect`.

```{r numeric}
as.numeric(pull(q2, rand_samp_pos))
as.numeric(pull(q2, char_vect))
as.numeric(pull(q2, factor_vect))
```

The mean outputs make sense based on the chunk above because the character and factor vectors return "NA" since they do not contain any numerical values that can be averaged.  The logical vector does return a mean because the values are binarized.
